A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management

### 2022-06-17 papers/paper/preprint.tex
start incorporating written edits from klaus

% Figures
\usepackage{graphicx}
\usepackage[list=true]{subcaption}
\graphicspath{{../../plots/}{../../tikz/}{../../img/}}
\usepackage[section]{placeins} % require floats to appear in the section they are defined

@@

% authors
\usepackage{authblk}
\title{A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management}
\author[1]{James Doss-Gollin}
\author[2]{Klaus Keller}
\affil[1]{Department of Civil and Environmental Engineering, Rice University}https://www.overleaf.com/project/6165ef2754a6517ec4648164
\affil[2]{Thayer School of Engineering, Dartmouth College}
\renewcommand*{\Affilfont}{\normalsize\normalfont}

@@

\begin{abstract}
    Needs work
    \vspace*{10em}
\end{abstract}

@@

Critical infrastructure services in America are aging and inadequate, leading to high-impact failures under conditions known to be possible \citep[\eg,][]{doss-gollin_txtreme:2021,doss-gollin_fatalism:2020}.
Looking to the future, it is expected that changes to regulation, economics and finance, patterns of population and infrastructure use, and climate will further stress infrastructure systems.
This motivates the question of which of many possible futures futures infrastructure systems and components should be designed for.
The answer to this question depends in part on values: intrinsic trade-offs between safety, performance, cost, and other objectives depend on context and stakeholder preferences \citep{keller_management:2021}.
However, this decision is also subject to assumptions regarding the likelihood and relevance of possible futures.\klaus{Vivek suggests spelling this out in a bit more detail}

@@

Currently used methods for estimating these \glspl{pdf} emphasize data-driven, nominally objective methods that can be applied consistently across locations.
For example, \gls{usgs} Bulletin 17C specifies procedures for estimating flood frequency and \gls{noaa} Atlas 14 provides estimates of the intensity, duration, and frequency of extreme rainfall.
Among several statistical assumptions these analyses make that have been recently called into question \citep[see][for a review]{Merz:2014gf} is stationarity (the assumption that past and future hazard come from the same \gls{pdf}).
For example, clear trends in extreme rainfall are apparent across much of southeastern Texas \citep{fagnant_spatiotemporal:2020,nielsen-gammon_txrainfall:2020}, and trends in many other hazards are consistent with observations \citep[see][for a comprehensive summary]{ipcc_impacts:2022}.
While some methods have been proposed for incorporating trends into these analyses \citep[see][for a review]{Salas:2018ge}, these assume specific forms of nonstationarity which may not fully represent physical processes or true levels of uncertainty \citep{DossGollin:2019,Montanari:2014hl,Serinaldi:2015bq}.
Ultimately, the difficulty of incorporating nonstationarity into existing frameworks has led to continued reliance on stationarity despite recognition of the associated limitations (see \cite{bulletin17c:2019}, p.~2, or \cite{atlas14_texas:2018} p.~A.4-42).

>>>>

% Figures
\usepackage[demo]{graphicx}
\usepackage[list=true]{subcaption}
\graphicspath{{../../plots/}{../../tikz/}{../../img/}}
\usepackage[section]{placeins} % require floats to appear in the section they are defined

@@

% authors
\usepackage{authblk}
\title{A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management}
\author[1]{James Doss-Gollin}
\author[2]{Klaus Keller}
\affil[1]{Department of Civil and Environmental Engineering, Rice University}
\affil[2]{Thayer School of Engineering, Dartmouth College}
\renewcommand*{\Affilfont}{\normalsize\normalfont}

@@

\begin{abstract}
    Current practice in engineering, infrastructure design, and local governance relies heavily upon standards that specify particular design events or conditions that buildings and infrastructure should safely withstand.
    The
\end{abstract}

@@

Many critical infrastructure services around the world are aging and inadequate for a changing climate \citep[\eg,][]{doss-gollin_txtreme:2021,doss-gollin_fatalism:2020,chester_reliable:2020}.
Looking to the future, it is expected that changes to regulation, economics and finance, patterns of population and infrastructure use, as well as climate, will further stress infrastructure systems.
This motivates the question: which possible futures should infrastructure systems and components be designed for?
The answer to this question depends in part on values: intrinsic trade-offs between safety, performance, cost, and other objectives depend on context and stakeholder preferences \citep{keller_management:2021} and are often regulated by statue or industry guidelines.
For example, hospitals and critical infrastructure are generally designed to a higher standard of risk protection than ordinary buildings.
At the same time, performance depends upon future conditions, and so decisions about which scenario to design for are necessarily subject to implicit or explicit assumptions about the likelihood or possibility of different future conditions.

@@

Currently used methods for estimating these \glspl{pdf} emphasize data-driven, nominally objective methods that can be applied consistently across locations.
For example, \gls{usgs} Bulletin 17C specifies procedures for estimating flood frequency and \gls{noaa} Atlas 14 provides estimates of the intensity, duration, and frequency of extreme rainfall.
Among several statistical assumptions these analyses make that have been recently called into question is stationarity \citep[the assumption that past and future hazard come from the same \gls{pdf}; see][for a review]{milly_stationarity:2008,merz_review:2014}.
For example, clear trends in extreme rainfall are apparent across much of southeastern Texas \citep{fagnant_spatiotemporal:2020,nielsen-gammon_txrainfall:2020}, and trends in many other hazards are consistent with observations \citep[see][for a comprehensive summary]{ipcc_impacts:2022}.
While some methods have been proposed for incorporating trends into these analyses \citep[see][for a review]{Salas:2018ge}, these assume specific forms of nonstationarity which may not fully represent physical processes or true levels of uncertainty \citep{DossGollin:2019,Montanari:2014hl,Serinaldi:2015bq}.
Ultimately, the difficulty of incorporating nonstationarity into existing frameworks has led to continued reliance on stationarity despite recognition of the associated limitations (see \cite{bulletin17c:2019}, p.~2, or \cite{atlas14_texas:2018} p.~A.4-42).
